A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises

### 2018-05-07 paper.tex
Revisions to paper through Implementation, also wrote Acknowledgements and Ethics

\documentclass[pageno]{jpaper}

\newcommand{\Semester}{Spring}
\newcommand{\IWreport}{2018}
\newcommand{\quotes}[1]{``#1''}
\makeatletter
\def\verbatim@font{\linespread{1}\normalfont\ttfamily}
\makeatother
\clubpenalty9998
\widowpenalty9999

@@

\thispagestyle{empty}
\doublespacing{}
\begin{abstract}
  Student interest in Princeton's undergraduate course in algorithmic game theory, ``Economics and Computing'' (COS 445), has grown rapidly in recent years.
  This course employs small simulations to develop students' ability to use theoretical tools to analyze more real-world situations.
  These strategy design exercises require considerably more software infrastructure than would a usual theoretical problem set, including handout code for student self-evaluation and software autograders.
  While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly structured assignments and evaluating student submissions in the context of each other.
  In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary components of these strategy design assignments.
  Concurrently, in my role as a grader for COS 445, I used the framework to develop and evaluate four strategy design assignments, using assignment specifications developed with Professor Weinberg.
  This provides feedback from real student and instructor users which was used to improve the design.
  Empirical results demonstrate the importance of quality tooling to effective use of instructor time, low broken submission rates, and high student satisfaction.
\end{abstract}

\newpage
\section*{Introduction}
My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course.
The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally, within healthy incentive structures where students do not try to hurt each others’ performance.
Each past offering of the course has rebuilt these assignments from scratch, and all associated instructor tooling, resulting in unnecessarily high allocation of instructor time to grading.
Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
In order to eliminate unnecessary annual replication of previous coursework development, improve course performance at scale, and improve the course experience for the students, I develop an extensible framework to improve these strategy design exercises.

Four Princeton University departments offer courses in game theory: economics, politics, mathematics, and computer science.
While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
For instance, in the computer science department, COS 445, ``Economics and Computing'', places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
This is represented in the course topics, which focus on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
It is also represented in the design of the problem sets, which contain, in addition to traditional proof-based exercises, programming-based exercises which connect course topics to prerequesite computer science skills.
These programming-based exercises take a common form.

Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java iterface}, in which two players must collaborate to receive the best outcome, but are each incentivized to defect, which results in a less preferred outcome, and have acecss to the other player's play history when making their own decision.
While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including, from semester to semester, a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
These examples are not exhaustive, but illustrate the variety of course topics with potential for translation to iterated games.

Students then craft strategies to play the specified game, based on their own analyses of the game's equilbirium, and based on their own priors over the strategies which will be designed by their peers.
These strategies are evaluated on both on their design quality and on their empirical performance.
While design quality is evaluated on a purely individual basis, empirical performance is measured by simulating the play of the collection of submitted student strategies.
For instance, for the iterated prisoner's dilemma, every student strategy plays one full game (consisting of many iterations of the prisoner's dilemma) against each other strategy, and strategies are scored based off the average payoff they achieved.
For the search advertisement game, all the student strategies are concurrently asked to bid on the same search terms, and are scored based on their revenue from ad clicks (where each bidder knows the click-through rate for a term prior to bidding on that term) less their expenditures on advertising.
To create a more realistic simulation, students are graded solely the performance of their own strategy, not on a curve of the performance of their peers.
That is, student grades on these strategy design exercises are not zero-sum.

While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demanded considerable instructor resources be dedicated to building and grading software resoruces, which have historically been significantly rebuilt for each assignment.
Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
Due to the limited tooling provided in past semesters for students to evaluate their submissions, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.

The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors creating new exercises to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.

Through this work, I aim to improve the quality of computer science theory education, from the perspectives of both the students and faculty associated with COS 445.
Quantitative metrics, including software failure rates and instructor time usage, and qualitiative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.

\section*{Related Work}
This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.\footnote{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
In one problem set, students developed and implemented strategies for three different strategy design exercises, related to three different classical games: Prisoner's Dilemma, Centipede, and Ultimatum.
In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{an auction of multiple items, one after another, where the winning bid pays the second highest bid. This is the auction format used by Google to sell sponsored search auctions.}

Both problem sets were implemented and graded by Cyril Zhang\footnote{https://github.com/cyrilzhang}, a graduate student TA for the course.
Cyril developed interfaces, dummy implementations, and grader software for each strategy design exercise.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
However, this existing implementation of grader software for strategy design assignments is not modular and has to be completely rewritten for each assignment, and was designed for grader use only.
The student interfaces were documented, but the grader software was not documented for future re-use.
Additionally, some of the scripts and notebooks used by Cyril were not preserved and were not accessible as resources.
Thus, while these resources served as inspiration for this work and provided some assignment-specific code to my work developing specific assignments, I did not build directly on Cyril's code.

Previous to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014\footnote{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code respositories used by the course staff.
In both semesters, Yonatan Naamad\footnote{https://github.com/ynaamad/} was responsible for software development.

The only resources available from Fall 2012 were collected from the course Google Code repository.\footnote{https://code.google.com/archive/p/cos445-scripts/}
This repository contains incomplete Python skeleton code for a basic tournament.
This was uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but was not reused.

The Spring 2014 iteration of the course was developed on a private GitHub repository.\footnote{https://github.com/ynaamad/cos445}
Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
The Java code consisted of student handouts of interfaces and some testing code, but the testing code was not designed to be automated for grading and was not modular: it tested manually-enterred strategies against each other and assignment-specific details (e.g.\ game structure and payoffs) were integrated within the simulation code.
As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
These resources were uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.

Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.

Harvard's Computer Science 136, ``Economics and Computation'',\footnote{https://beta.blogs.harvard.edu/k108875/assignments/} assigns two programming problem sets.
The first requires implementation of a peer-to-peer filesharing system similar to Bittorrent, a protocol in which incentives parallel Prisoner's Dilemma.
However, the assignment is not a competition and student solutions are not differentiated based on strategic properties.
The second assignment is a strategy design exercise built on the generalized second-price auction, in which student strategies vary and are graded based on their performance in a competitive environment.
This is very similar to both the Spring 2014 and Spring 2017 auction exercises of COS 445 at Princeton.
However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and the implementation is in Python.
While comparison between COS 445 assignments and CS 136 assignments in a future project might provide some pedagogical value, such work would be out of scope for this project.
Given that these assignments are implemented in Python, only handout (and not grading) code is available, and the assignments are graded differently, these resources were dismissed as a base for development of new resources for COS 445 at Princeton.

Many universities, including Princeton, maintain extensive systems for the automatic submission and processing of student assignments.
Such resources are useful in the general case of developing new programming-based assignments, but no such resources replicate the behavior implemented in this project.
Most autograding systems are designed with an assumption that student submission are graded in a sandbox, isolated from other student submissions.
Such systems are not applicable to this project, since the strategy design exercises involve evaluation of student strategy performance in a common environment.
However, existing resources for assignment submission and student feedback in use by Princeton are used in this assignment.
I integrated some CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and modelled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
Generally, however, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.

\section*{Approach}
Cyril Zhang completed the TA requirement for the PhD program last fall, so at the start of this semester it was unclear who among the graduate and undergraduate course staff would be responsible for maintaining these assignments.
Thus, the course needed not just long-term work to improve student and instructor resources, but also short-term work to maintain and debug the same resources.
These harmonizing requirement suggest that the product should consist of one extensible implementation of all the reusable components for software design exercises, developed iteratively in conjunction with its usage in the course.
This software would naturally grow throughout development as demanded by the needs of the course, and the final product will naturally lower-bound the maximum degree of automation and modularity possible.

Before the first problem set of the course was assigned in this semester, Matt and I designed and I implemented a handout interface and tools to allow students to test their strategies against each other.
The game simulates college admissions using stable matchings.
While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design covered in previous courses.\footnote{Kernighan and Pike chapter 4}
I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which amortized results from multiple randomized trials, and from agglomerated these results to output performance statistics for students.
Thus, when it came time to implement the second strategy design exercise, I was able to reuse code which processed results of trials, even though the nature of the trails changed from college admissions to elections.
Additionally, when it came time to grade the problem set, I was able to modify only the post-processing step to compute grades.
Thus, creating a new assignment requires constant work in the number of framework extensions, and creating a new framework extension requires constant work in the number of assignments.

The result of this process duplicates significant functionality from last year's assignments.
However, because of conscious design decisions to factor our repeated code from assignment implementations, it accomplishes what previous implementations had not.
It will be modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
Throughout the semester, I can leverage my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
And, it will be reusable, both for the same assignments in future years, and for new strategy design exercises implemented by future course staff with lower overhead.

In order to increase the reusability, I elected to store it in a University-owned private GitHub repository.
This ensures that, even after I have graduated, future course staff will have access to the project.
Additionally, I documented the repository structure and each program's role in the repository, as documented later in this document.

\section*{Implementation}
The first key decision in the implementation of these programming assignments was language selection.
Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results}, and this would be preferred by the course staff as well.
Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parametrized on user-input strategy names.
Unfortunately, COS 445 does not have Python experience as a course prerequisite, only Java experience.
Additionally, survey data from other course surveys suggests that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python.\footnote{COS 333 survey data}

Thus, the whole system under consideration is constrained: it must support student strategy implementations in Java.
Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignments as possible in Java, with limited usage of scripting languages such as make, Python, and bash.
These scripting languages were used where Java would not suffice and only for tasks for which implementation details were irrelevant to student assignment comprehension.

Java also offers convenience to assignment designers by enforcing an object-oriented design pattern.
This allows instructors to communicate an assignment specification formally through a well-documented interface.
Furthermore, by constructing new instances of the student implementations between game rounds, instructors can programatically enforce that students do not employ learning strategies outside the parameters of the assignment.\footnote{This requires that instructors forbid the usage of static variables, but it is trivial to verify compliance with this requirement.}

However, several default Java behaviors do not map cleanly onto the desired properties of strategy design exercises.
For instance, Java objects used as function parameters are passed by mutable, nullable reference.
This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and not null unless otherwise explicitly specified.
Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
In order to preserve backwards compatibility, these features are not implemented by default.
Where possible, I have taken advantage of these features.
Since the assignment specification documents that students are required not to modify parameters, instructor code can use unmodifiable (immutable) containers.
However, I have not included NotNull annotations because they are not taught in the prerequesite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.\footnote{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}

In order to design my framework, I reviewed unmodularized code from a past strategy design exercise, the Spring 2017 auctions exercise.
This is the only assignment to which I had access to the full implementation of the student handout (having taken the course) and the grader code (preserved by Professor Weinberg).
The first piece of the assignment to be implemented, after the game design is complete, is the student interface:\footnote{TODO: make this code a figure}
\begin{verbatim}
import java.util.List;

@@

    // Let you know if you won, and how much the winners paid
    // Called once per day after the auction
    public void addResults(List<Double> bids, int myBid, double myPayment);
}
\end{verbatim}
This interface describes what students' strategies must do: they must, each day, bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results''), and they value the word being auctioned each day at a different value.
The strategy also has access the winning bids for each of the ten sponsored results from each past day, and knows if it won any auctions itself, and if so how much it paid.
This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
These constants are not documented in the interface as designed, only in the assignment specification.
The instructors distribute a simple sample student implementation, in this case the truthful bidder.
Cyril also implemented a program used to grade the student-submitted strategies.
This program had two methods: \texttt{main} and \texttt{trial}.
The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
The latter contained an implementation of the generalized second-price auction format described in the assignment specification.

>>>>

\documentclass[pageno]{jpaper}
%%% Local Variables:
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
\newcommand{\Semester}{Spring}
\newcommand{\IWreport}{2018}
\newcommand{\quotes}[1]{``#1''}

\usepackage{minted}
\setminted{baselinestretch=1}

\clubpenalty9998
\widowpenalty9999

@@

\thispagestyle{empty}
\doublespacing{}
\begin{abstract}
  Student interest in ``Economics and Computing'', Princeton's undergraduate computer science course in algorithmic game theory, has grown rapidly in recent years.
  This course employs small simulations to develop students' ability to use theoretical tools to analyze more real-world situations.
  These strategy design exercises require considerably more software infrastructure than a usual theoretical problem set would, including handout code for student self-evaluation and software auto-graders.
  While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly structured assignments and evaluating student submissions in the context of each other.
  In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary components of these strategy design assignments.
  Concurrently, in my role as a grader for COS 445, I used the framework to develop and evaluate four strategy design assignments, using assignment specifications developed with Professor Weinberg.
  This provides feedback from real student and instructor users which was used to improve the design.
  Empirical results demonstrate the importance of quality tooling to effective use of instructor time, low broken submission rates, and high student satisfaction.
\end{abstract}

\newpage
\section*{Introduction}
My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course, COS 445 ``Economics and Computing''.
The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally within a healthy incentive structure where students do not try to hurt each others’ performance.
Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
In order to eliminate unnecessary annual replication of previous coursework development, improve course performance at scale, and improve the course experience for students, I developed an extensible framework to improve these strategy design exercises.

Four Princeton University departments offer courses in game theory: Economics, Politics, Mathematics, and Computer Science.
While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
These programming-based exercises take a common form.

Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java interface}, in which two players must collaborate to receive the best outcome, but are each incentivized to defect, which results in a less preferred outcome, and have access to the other player's previous decisions when making their own decision.
While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
These examples are not exhaustive, but illustrate the variety of course topics with potential for translation to iterated games.

Students then craft strategies to play the specified game, based on their own analyses of the game's equilibrium and on which strategies they expect their peers to play.
These strategies are evaluated on both on their design quality and on their empirical performance.
While design quality is evaluated on a purely individual basis, empirical performance is measured by simulating the play of the collection of submitted student strategies against each other.
For instance, for the iterated prisoner's dilemma, every student strategy plays one `full' game, consisting of many iterations of the prisoner's dilemma, against each other student strategy.
Strategies are scored based off the average payoff they achieve.
For the search advertisement game, all the student strategies are concurrently asked to bid on the same search terms.
They are scored based on their revenue from ad clicks less their expenditures on advertising, and each bidder knows the click-through rate for a term prior to bidding on that term.
To create a more realistic simulation, students are graded solely on the performance of their own strategy, not on a curve of the performance of their peers.
That is, student grades on these strategy design exercises are not zero-sum.

While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand considerable instructor resources be dedicated to building and grading software resources, which have historically been significantly rebuilt for each assignment.
Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
Due to the limited tooling provided in past semesters for students to test their code, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.

%TODO: move the above into the body / approach and the above as the introduction
The goals of this project are to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition.
This was accomplished by designing a reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, and to develop advanced automated grading tools than previously existed for the course.
Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.

Through this work, I aim to improve the quality of computer science theory education from the perspectives of both the students and faculty associated with COS 445.
Quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.

\section*{Related Work}
This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.\footnote{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different classical games: Prisoner's Dilemma, Centipede, and Ultimatum.
In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{an auction of multiple items, one after another, where the winning bid pays the second highest bid. This is the auction format used by Google to sell sponsored search auctions.}

Both problem sets were implemented and graded by Cyril Zhang\footnote{https://github.com/cyrilzhang}, a graduate student TA for the course.
Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
However, his implementation of software for strategy design assignments was intended for grader use only.
It is not modular and has to be completely rewritten for each assignment.
The student interfaces were documented, but the grader software was not documented for future use.
Additionally, some of the scripts and notebooks used by Zhang were not preserved and were not accessible as resources.
Thus, while these resources served as inspiration for this work and provided some assignment-specific code to my work developing specific assignments, I did not build directly on Zhang's code.

Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014\footnote{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code repositories used by the course staff.
In both semesters, Yonatan Naamad\footnote{https://github.com/ynaamad/} was responsible for software development.

The only resources available from Fall 2012 were collected from the course Google Code repository.\footnote{https://code.google.com/archive/p/cos445-scripts/}
This repository contains incomplete Python skeleton code for a basic tournament of an unspecified game.
I uploaded this code to the current course repository\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but did not develop it further.

The Spring 2014 iteration of the course was developed on a private GitHub repository.\footnote{https://github.com/ynaamad/cos445}
Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
The Java code was the student handout, which contained strategy interfaces and some testing code.
The testing code was not designed to be automated for grading and was not modular.
It tested manually-entered strategies against each other, and assignment-specific details, such as game structure and payoffs, were integrated within the simulation code.
As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
These resources were uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.

Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke,\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.

Harvard's Computer Science 136, ``Economics and Computation'',\footnote{https://beta.blogs.harvard.edu/k108875/assignments/} assigns two programming problem sets.
The first requires implementation of a peer-to-peer file sharing system similar to Bittorrent, a protocol in which incentives parallel Prisoner's Dilemma.
However, the assignment is not a competition and student solutions are not differentiated based on strategic properties.
The second assignment is a strategy design exercise built on the generalized second-price auction, in which student strategies vary and are graded based on their performance in a competitive environment.
This is very similar to both the Spring 2014 and Spring 2017 auction exercises of COS 445 at Princeton.
However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and that the implementation is in Python.
While comparison between COS 445 assignments and CS 136 assignments in a future project might provide some pedagogical value, such work would be out of scope for this project.
Given that these assignments are implemented in Python, only handout (and not grading) code is available, and the assignments are graded differently, these resources were dismissed as a base for development of new resources for COS 445.

Many universities, including Princeton, maintain extensive systems for the automatic submission and processing of student assignments.
Such resources are useful in the general case of developing new programming-based assignments, but no such resources replicate the behavior implemented in this project.
Most auto-grading systems are designed with an assumption that each student submission is graded in isolation from other student submissions.
Such systems are not applicable to this project since the strategy design exercises involve evaluation of student strategy performance in a common environment.
Though existing automatic grading systems cannot replicate the full extend of this work, I integrate existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
I integrated CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
Generally, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.

\section*{Approach}
Cyril Zhang completed the TA requirement for the PhD program last fall, so at the start of this semester it was unclear who among the graduate and undergraduate course staff would be responsible for maintaining the COS 445 strategy design exercises.
Therefore, the course needed not just long-term work to improve student and instructor resources, but also short-term work to maintain and debug the same resources.
These coinciding requirements inspired me to design one extensible implementation of all the reusable components for software design exercises, and to develop the project iteratively in conjunction with its usage in the course.
This software would naturally grow throughout development as demanded by the needs of the course, and the final product will naturally lower-bound the maximum degree of automation and modularity possible.

Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
The game simulates college admissions using stable matchings.
While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.\footnote{Kernighan and Pike chapter 4}
I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.
When it came time to implement the second strategy design exercise, I was able to reuse code which processed results of trials, even though the nature of the trials changed from college admissions to elections.
Additionally, when it came time to grade the problem set, I was able to modify only the post-processing step to compute grades.
Thus, creating a new assignment required constant work in the number of framework extensions, and creating a new framework extension requires constant work in the number of assignments.
% TODO: maybe put stuff from earlier here?
The result of this process duplicates significant functionality from last year's assignments.
However, because of conscious design decisions to factor out repeated code from assignment implementations, it accomplishes what previous implementations had not.
It will be modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
Throughout the semester, I can leverage my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
It will be reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.

In order to increase the reusability, I elected to store it in a University-owned private GitHub repository and documented the repository structure and contents.
This ensures that future course staff will have the physical and technical means to maintain this project after I have graduated.

\section*{Implementation}
% TODO: signposting
The first key decision in the implementation of these programming assignments was language selection.
Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results}, and this would be preferred by the course staff as well.
Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parameterized on user-input strategy names.
Unfortunately, COS 445 only prerequisites Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.\footnote{COS 333 survey data}

Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
These scripting languages were used only where Java would not suffice and only where implementation details were irrelevant to student assignment comprehension.

Java also offers convenience to assignment designers by enforcing an object-oriented design pattern.
This allows instructors to communicate assignment specifications formally through a well-documented interface.
Furthermore, by constructing new instances of student implementations between game rounds, instructors can programatically enforce that students do not employ learning strategies outside the parameters of the assignment.\footnote{This requires that instructors forbid the usage of static variables, but it is trivial to verify compliance with this requirement.}

However, several default Java behaviors do not map cleanly onto the desired properties of strategy design exercises.
For instance, Java objects used as function parameters are passed by mutable, nullable reference.
This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and nonnull unless otherwise explicitly specified.
Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
In order to preserve backwards compatibility, these features are not implemented by default.
Where possible, I have taken advantage of these features.
Since the assignment specification documents that students are required not to modify parameters, instructor code can use unmodifiable (immutable) containers.
However, I have not included NotNull annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.\footnote{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}

\subsection*{Handout Implementation}
In order to design my framework, I reviewed non-modularized code from the Spring 2017 auctions exercise.
This is the only assignment for which I had access to both the student handout and the grader code.
After the game design is complete, the first piece of the assignment to be implemented is the student interface:\footnote{TODO:\ make this code a figure}
\begin{minted}{java}
import java.util.List;

@@

    // Let you know if you won, and how much the winners paid
    // Called once per day after the auction
    public void addResults(List<Double> bids, int myBid, double myPayment);
}
\end{minted}
This interface describes the necessary functions of a student strategy.
Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results''), and they assign different values to words auctioned on different days.
The strategy also has access the winning bids for each of the ten sponsored results from each past day and which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
These constants are not documented in the interface as designed, only in the assignment specification.
The instructors distribute a simple sample student implementation --- in this case, the truthful bidder.
Zhang also implemented a program used to grade the student-submitted strategies, which consisted of two methods: \texttt{main} and \texttt{trial}.
The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
The latter contained an implementation of the generalized second-price auction format described in the assignment specification.
